---
title: "taxa_landing"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Taxa navigating page

Search for the taxon you are interested with. You will be redirected for a new page

<input type="text" id="filterInput">
<button onclick="filterSearch()">Search</button>
<div id="suggestions"></div>

<script>
var links = {
  Google: "https://www.google.com",
  Wikipedia: "https://www.wikipedia.org",
  ChatGPT: "https://openai.com/ai-service-products/#chat",
  Youtube: "https://www.youtube.com"
};

function filterSearch() {
  var input = document.getElementById("filterInput").value;
  for (var tag in links) {
    if (input === tag) {
      window.open(links[tag], "_blank");
      break;
    }
  }
}

document.getElementById("filterInput").addEventListener("input", showSuggestions);

function showSuggestions() {
  var input = document.getElementById("filterInput").value;
  var suggestions = document.getElementById("suggestions");
  suggestions.innerHTML = "";
  for (var tag in links) {
    if (tag.toLowerCase().startsWith(input.toLowerCase())) {
      var suggestion = document.createElement("div");
      suggestion.innerHTML = tag;
      suggestion.addEventListener("click", function() {
        document.getElementById("filterInput").value = this.innerHTML;
        suggestions.innerHTML = "";
      });
      suggestions.appendChild(suggestion);
    }
  }
}

</script>

### Here are some correlation heatmaps for each taxa
To better visualize, the origianl heatmap was divided by four sections

```{r message=FALSE}
library(qtlcharts)
#our data
data <- read.delim("C:/Users/henri/Desktop/Soil_Microbiome/sandbox/mock_all_data.txt")

#only taxa, must be edited when using real data
data_taxa <- data[,c(1:21)]

#name rows as ID
rownames(data_taxa) <- data_taxa$Sample_ID
data_taxa_clean <- data_taxa[, c(2:ncol(data_taxa))]

#coercing into a matrix
matrix_taxa<- as.matrix(data_taxa_clean)

#get biomes vector
biomes <- factor(data$Biome)

#correlation and ordering
spearman <- cor(data_taxa_clean, use="pairwise.complete.obs", method="spearman")
ord <- hclust(as.dist(-spearman))$order

#setting postions for sectorizing
if(length(ord)%%2 ==0)
  {
  first_half <- length(ord)/2
  second_half <- (length(ord)/2)+1
  end <- length(ord)
} else {
  first_half <- length(round(ord/2))
  second_half <- (length(round(ord/2))+1)
  end <- length(ord)
  }

#filter spearman matrix by value
#spearman_filtered<-which(abs(spearman) >= 0.2 )

#ploting first quarter
iplotCorr(data_taxa_clean[,ord],
                      biomes, 
                      corr=spearman[ord[c(1:first_half)],ord[c(1:first_half)]],
                      chartOpts=list(scatcolors= RColorBrewer::brewer.pal(6,"Set2")))

#ploting second quarter
iplotCorr(data_taxa_clean[,ord],
                       biomes,
                       corr=spearman[ord[c(1:first_half)],ord[c(second_half:end)]],
                       chartOpts=list(scatcolors= RColorBrewer::brewer.pal(6,"Set2")))

#ploting third quarter
iplotCorr(data_taxa_clean[,ord],
                       biomes,
                       #reorder=TRUE, 
                       corr=spearman[ord[c(second_half:end)],ord[c(1:first_half)]],
                       chartOpts=list(scatcolors= RColorBrewer::brewer.pal(6,"Set2")))


#ploting fourth quarter
iplotCorr(data_taxa_clean[,ord],
                       biomes,
                       #reorder=TRUE, 
                       corr=spearman[ord[c(second_half:end)],ord[c(second_half:end)]],
                       chartOpts=list(scatcolors= RColorBrewer::brewer.pal(6,"Set2")))


```
